\documentclass[10pt,journal,compsoc]{IEEEtran}

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{CS 6600 Project Report: Unmanned Aircraft System}

\author{Matthew Whitesides and Bruce M. McMillin \\
Department of Computer Science \\
Missouri University of Science and Technology, Rolla, MO 65409-0350}

% The paper headers
\markboth{Missouri S\&T COMP\_SCI 6600: Formal Methods in CmpSec, Fall~2021}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

% The paper abstract
\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}}

% make the title area
\maketitle

\IEEEpeerreviewmaketitle

%-------------------------------------------------------------------------

\section{Infrastructure}

\subsection{Infrastructure Description}

\IEEEPARstart{I}{n} its simplest form, an unmanned aircraft system (UAS), is an aircraft system that operates without an onboard pilot. 
UAS are either controlled remotely through some form of wireless radio communication, semi-autonomously in conjunction with a remote pilot, or fully autonomously using some form of computational intelligence as navigation. 
These intelligent crewless vehicles have many potential uses in the defense sector, including surveillance, strategic mission execution, aerial sustainability support, and training systems, to name a few. 
These aircraft fall under the umbrella of cyber-physical systems (CPS), merging the intelligent navigation processes, system health monitoring, and communication with the physical mobile ariel vehicle.

We will design a proposed infrastructure security policy for the Boeing MQ-25 unmanned aircraft system, but it will also apply to similar mission support drones. 
The MQ-25 is an unmanned aircraft system designed for the U.S. Navy, and it provides autonomous refueling capability for the Boeing F/A-18 Super Hornet, Boeing EA-18G Growler, and Lockheed Martin F-35C fighters.
This capability extends the combat range of the supported aircraft, seamlessly and semi-anonymously navigating to the plane, refueling, and returning to base. 
MQ-25 is the first unmanned aircraft to support aerial refueling another aircraft and is currently in the flight test phase of development [1], making it the perfect system to analyze security impacts for current and future unmanned aircraft systems. 

% \subsection{Rights Leakages}

% text

% \subsubsection{Confidentiality}

% text

% \subsubsection{Integrity}

% text

% %-------------------------------------------------------------------------
% \section{Survey}
% The various models will be surveyed below.

% %-------------------------------------------------------------------------
% \subsection{HRU}

% \begin{small}
% Access Control Matrix:
% \end{small}

% \begin{figure}[h]
% \begin{tiny}
% \noindent
% \begin{tabular}{|c|c|c|c|c|}
% \hline Objects / Subjects  & Vehicle & Central Authority & Authorized Client & Unauthorized Client \\
% \hline Vehicle &  &  &  &  \\
% \hline Central Authority &  &  &  & \\
% \hline Authorized Client &  & C/D/W & R &  \\
% \hline Unauthorized Client &  & C/D/W &  &  \\
% \hline GPS Location & W &  & R &  \\
% \hline Destination & W &  & R &  \\
% \hline Path & R &  & W &  \\
% \hline

% \end{tabular}
% \end{tiny}
% \caption{ACM Table of the HRU model. Objects vertically and subjects horizontally}

% \end{figure}

% \begin{small}

% Commands that cause rights leakage:

% enter R into ACM[Unauthorized Client, Vehicle];

% enter R into ACM[Unauthorized Client, GPS Location];

% enter R into ACM[Unauthorized Client, Destination];

% enter W into ACM[Unauthorized Client, Path];
% \end{small}

% \subsection{T-G}
% text
% \subsection{BLP}
% text
% \subsection{Biba}
% text
% \subsection{Noninference/Noninterference/ NonDeducibility}
% text
% \section{Specific Models and Rights Leakages}
% \subsection{HRU}
% text
% \subsection{T-G}
% text
% \subsection{BLP}
% text
% \subsection{Biba}
% text
% \subsection{Noninference}
% text
% \subsection{Noninterference}
% text
% \subsection{NonDeducibility}
% text
% \subsection{MSDND}
% text

% \section{Specific Models and Rights Leakages}
% \subsection{HRU}
% text
% \subsection{T-G}
% text
% \subsection{BLP}
% text
% \subsection{Biba}
% text
% \subsection{Noninference}
% text
% \subsection{Noninterference}
% text
% \subsection{NonDeducibility}
% text
% \subsection{MSDND}
% text

% \begin{figure}[h]
%    \caption{Example of caption.}
% \end{figure}

% \section{Conclusions}

% Provide a summative conclusion on the modeling of your infrastructure.

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
A.~Erwin, and J.~Gibson, Navy, Boeing Make Aviation History with MQ-25 Becoming the First Unmanned Aircraft to Refuel Another Aircraft, Accessed on: Sept. 1, 2021. [Online]. Available: https://www.boeing.com/defense/mq25/ 

\end{thebibliography}

% biography section
\begin{IEEEbiographynophoto}{Matthew Whitesides}
  Master's Student at Missouri University of Science and Technology.
\end{IEEEbiographynophoto}

% that's all folks
\end{document}


